\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-26 exps.tex
exprs

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot coordinates {(HRTCS,1)(Printer/CD1,1.6)(Printer/CD2,1)(AECS/CD1,4.25)(AECS/CD2,4.25)};
			\addplot coordinates {(Printer/CD2, 1)(AECS/CD2, 4.25)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={Motor},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot coordinates {(Motor, 3.54)};
			\addplot coordinates {(Motor, 3.15)};
			\addplot coordinates {(Motor, 4.46)};
			\addplot coordinates {(Motor, 3.35)};
			\addplot coordinates {(Motor, 2.81)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			ymajorgrids=true,
			ytick={0,...,5},
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot coordinates
			{(HRTCS,1)(Printer/CD1,1.6)(Printer/CD2,1)(AECS/CD1,4.25)(AECS/CD2,5.39)};
			\addplot coordinates {(Printer/CD2, 1)(AECS/CD2, 5.39)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,...,5},
			ymin={1.5},
			minor y tick num=1,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot coordinates {(Motor, 3.54)};
			\addplot coordinates {(Motor, 3.15)};
			\addplot coordinates {(Motor, 4.46)};
			\addplot coordinates {(Motor, 3.35)};
			\addplot coordinates {(Motor, 2.81)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph}
\end{figure}

There are two main reasons that influence size of the relaxation: 1)
execution speed of a target platform 2) and the nature of the program
which runs on that specific platform. As one can easily speculate, clock
frequency of the processor directly impacts on the value of WCRT. On the
other hand, programmer can write a program such that large data
computation in a single tick increases WCRT of the program. Assuming we
do not change the architecture of the execution platform (i.e. JOP), the
difference factor can only be reduced by modifying the benchmark
programs by dividing the single longest tick, that corresponds to WCRT,
into a number of smaller ticks.
